|

### 2021-01-30 appendix/appendix.Rmd
add more analyses to experiment 01

---
title: |
       | Supplementary Materials for "Casting the First Stone: Understanding Attitudes towards Lynching in Brazil"
author:
- "Danilo Freire[^freire]"
- "David Skarbek[^skarbek]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: yes
    template: template.latex
---

@@

\footnotesize
```{r loading, warning=F, error=F, cache=T}
# Install and load required packages
packages <- c("cjoint", "cregg", "kableExtra",
              "janitor", "stargazer", "tidyverse")
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

@@

                          "concordo"     = "Agree",
                          "não concordo" = "Disagree"),

@@

```{r samplesize, echo=F, warning=F, error=F, cache=T}
df1 <- df %>% filter(consent == "Agree")
```

@@

```{r incometext, echo=F, warning=F, error=F, cache=T}
df2 <- df1 %>%
  group_by(household_income) %>%
  filter(!is.na(household_income)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(`Household Income` = household_income)
```

@@

\footnotesize
```{r deathpenalty, warning=F, error=F, cache=T}
df1 %>%
  group_by(death_penalty) %>%
  filter(!is.na(death_penalty)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(`Support for Death Penalty` = death_penalty) %>%
  kbl(., booktabs = TRUE,  linesep = "",
      caption = "Support for Death Penalty") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

Respondents indicated which profile they preferred for extrajudicial
punishment. They had read the following prompt prior to the experiment:

@@

## Replication Code

We estimate the conjoint experiments with the `cregg` package
[@leeper2018cregg] for the `R` statistical language [@rstats2019]. We follow
@leeper2018subgroup and report marginal means

We will cluster standard errors by
respondent. The code follows below.

\footnotesize
```{r conjointfull, warning=F, error=F, cache=T, fig.width=7, fig.height=6}
conjoint_data <- read.qualtrics("../data/data-conjoint.csv",
                                responses = c("Q13", "Q14", "Q15",
                                              "Q16", "Q17"),
                                covariates = c("ResponseId",
                                               "Q1", "Q2", "Q3", "Q4",
                                               "Q5", "Q6", "Q7",
                                               "Q8", "Q9", "Q10",
                                               "Q11", "Q12"),
                                new.format = FALSE, respondentID = NULL)

@@

fm <- selected ~ `Gender of crime perpetrator` +
  `Age of crime perpetrator` + `Race of crime perpetrator` +
  `Residency of crime perpetrator` + `Offense` +
  `Gender of crime victim` + `Age of crime victim` +
  `Lynching perpetrators`

faces <- c(rep("plain", 5), "bold",
           rep("plain", 4), "bold",
           rep("plain", 2), "bold",
           rep("plain", 5), "bold",
           rep("plain", 2), "bold",
           rep("plain", 4), "bold",
           rep("plain", 3), "bold",
           rep("plain", 2), "bold")

plot(mm(conjoint_data, fm, id = ~response_id),
     vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "none",
        axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)
```
\normalsize

>>>>

---
title: |
       | Supplementary Materials for "Casting the First Stone: Understanding Attitudes towards Lynching in Brazil"
author:
- "Danilo Freire[^freire]"
- "David Skarbek[^skarbek]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

@@

\footnotesize
```{r loading, warning=F, error=F, cache=F}
# Install and load required packages
packages <- c("cjoint", "cregg", "kableExtra",
              "janitor", "stargazer", "tidyverse")
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

@@

                          concordo     = "Agree",
                          `não concordo` = "Disagree"),

@@

```{r sample-size, echo=F, warning=F, error=F, message=F, cache=T}
df1 <- df %>% filter(consent == "Agree")
```

@@

```{r income-text, echo=F, warning=F, error=F, cache=T}
df2 <- df1 %>%
  group_by(household_income) %>%
  filter(!is.na(household_income)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(`Household Income` = household_income)
```

@@

\footnotesize
```{r death-penalty, warning=F, error=F, cache=T}
df1 %>%
  group_by(death_penalty) %>%
  filter(!is.na(death_penalty)) %>%
  summarise(N = n()) %>%
  mutate(Frequency = round(N / sum(N), 3)) %>%
  rename(`Support for Death Penalty` = death_penalty) %>%
  kbl(., booktabs = TRUE,  linesep = "",
      caption = "Support for Death Penalty") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "hold_position")
```
\normalsize

@@

We added three restrictions to the conjoint design to avoid implausible
scenarios. First, female rapists were excluded from the model, but we did
include female molesters in the conjoint experiment. Second, when the offense
was car theft, the victim could not be a child. Lastly, teenagers could not be
victims of car theft either. All other combinations were allowed. We randomized
the attributes using a `.php` script, which is available at
<https://github.com/danilofreire/lynching-experiment-brazil/blob/master/conjoint/portuguese/lynching-conjoint-pt.php>.

Respondents indicated which profile they preferred for extrajudicial
punishment. Prior to the experiments, they had read the following prompt:

@@

## Marginal Means Estimator

We estimate the conjoint experiment with the `cregg` package [@leeper2018cregg]
for the `R` statistical language [@rstats2019]. We follow @leeper2020measuring
and report marginal means as our main estimates. Marginal means are easy to
interpret and they are not sensitive to choice of the reference category in
subgroup analyses. The $H_0$ in all models are that the coefficient is equal to
0.5, that is, that respondents are indifferent to the attribute level. Standard
errors are clustered by respondent. The code follows below.

\footnotesize
```{r conjoint-mm, warning=F, error=F, message=F, cache=T, fig.width=7, fig.height=6}
conjoint_data <- read.qualtrics("../data/data-conjoint.csv",
                                responses = c("Q13", "Q14", "Q15",
                                              "Q16", "Q17"),
                                covariates = c("ResponseId",
                                               "Q1", "Q2", "Q3", "Q4",
                                               "Q5", "Q6", "Q7",
                                               "Q8", "Q9", "Q10",
                                               "Q11", "Q12"),
                                new.format = FALSE, respondentID = NULL)

@@

# Model
fm <- selected ~ `Gender of crime perpetrator` +
  `Age of crime perpetrator` + `Race of crime perpetrator` +
  `Residency of crime perpetrator` + `Offense` +
  `Gender of crime victim` + `Age of crime victim` +
  `Lynching perpetrators`

mms <- mm(conjoint_data, fm, id = ~response_id, h0 = 0.5)

# Plot
faces <- c(rep("plain", 5), "bold",
           rep("plain", 4), "bold",
           rep("plain", 2), "bold",
           rep("plain", 5), "bold",
           rep("plain", 2), "bold",
           rep("plain", 4), "bold",
           rep("plain", 3), "bold",
           rep("plain", 2), "bold")

plot(mms, vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "none",
        axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)

# Table
table_mm <- function(mms, capt) {
dfr <- data.frame(feature = mms[, c(4)],
                  round(mms[, c(5, 6, 8, 9, 10)], digits = 3))
names(dfr) <- c("Feature", "Estimate", "Std. Error",
                "P-Value", "Lower", "Upper")
return(kbl(dfr, "latex", caption = capt, linesep = "",
           booktabs = TRUE) %>%
kable_styling(font_size = 12, full_width = TRUE,
              latex_options = "hold_position") %>%
pack_rows("Gender of crime perpetrator", 1, 2) %>%
pack_rows("Age of crime perpetrator", 3, 5) %>%
pack_rows("Race of crime perpetrator", 6, 9) %>%
pack_rows("Residency of crime perpetrator", 10, 11) %>%
pack_rows("Offense", 12, 16) %>%
pack_rows("Gender of crime victim", 17, 18) %>%
pack_rows("Age of crime victim", 19, 22) %>%
pack_rows("Lynching perpetrators", 23, 27) %>%
column_spec(1, width = "6cm"))
}

table_mm(mms, capt = "Marginal Means -- Full Model")
```
\normalsize

## Average Marginal Component Effect (AMCE) Estimator

We also estimate AMCE coefficients for our conjoint experiment. This method
selects one reference category for each attribute and look at changes from the
baseline level. The reference category are marked as zero in our models.

\footnotesize
```{r conjoint-amce, warning=F, error=F, message=F, cache=T, fig.width=7, fig.height=6}
amces <- cj(conjoint_data, fm, id = ~response_id)

plot(amces, vline = 0.0, header_fmt = "%s") +
  theme(legend.position = "none",
        axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)

table_mm(amces, capt = "Average Marginal Component Effects -- Full Model")
```

## Subgroup Analyses

In this subsection, we test whether our results vary according to individual characteristics, such as gender, age, race, income, support for death penalty, and the respondents' opinions on the judicial system and the police forces. All models report marginal means.

### Gender

Results do not seem to vary according to the gender of the respondent. We focus
here on the differences between males and females and exclude the 11
observations in which respondents preferred not to say their gender or marked
"other" in our questionnaire. Across all conjoint experiment attributes, we see
that an overlap between the 95% confidence intervals for males and females.

\footnotesize
```{r conjoint-females, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.3, fig.pos = "H"}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(gender) %>%
  filter(gender == c("Male", "Female"))
cjdt$Gender <- factor(cjdt$gender)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
            h0 = 0.5, by = ~Gender)

# Plot
plot(mm_by, group = "Gender", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)

# Tables
table_mm_by <- function(mm_by, capt) {
dfr <- data.frame(feature = mm_by[, c(5)],
                  round(mm_by[, c(6, 7, 9, 10, 11)], digits = 3))
names(dfr) <- c("Feature", "Estimate", "Std. Error",
                "P-Value", "Lower", "Upper")
return(kbl(dfr, "latex", caption = capt, linesep = "",
           booktabs = TRUE) %>%
kable_styling(font_size = 12, full_width = TRUE,
              latex_options = "hold_position") %>%
pack_rows("Gender of crime perpetrator", 1, 2) %>%
pack_rows("Age of crime perpetrator", 3, 5) %>%
pack_rows("Race of crime perpetrator", 6, 9) %>%
pack_rows("Residency of crime perpetrator", 10, 11) %>%
pack_rows("Offense", 12, 16) %>%
pack_rows("Gender of crime victim", 17, 18) %>%
pack_rows("Age of crime victim", 19, 22) %>%
pack_rows("Lynching perpetrators", 23, 27) %>%
column_spec(1, width = "6cm"))
}

mm_females <- mm_by %>% filter(BY == "Female")
table_mm_by(mm_females, capt = "Marginal Means -- Females")
```

```{r conjoint-males, warning=F, message=F, error=F, cache=T, fig.pos = "H"}
mm_males <- mm_by %>% filter(BY == "Male")
table_mm_by(mm_males, capt = "Marginal Means -- Males")
```
\normalsize

### Age

As our age variable is continuous, we divide the data into three age brackets:
18-34 years old, 35-54 years old, and 55-plus years old. The results show that
seniors (55-plus) are more likely to select profiles that include murder as an
offense, and less inclined to choose cases

\footnotesize
```{r conjoint-age, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=5.5}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(age) %>%
  mutate(age2 = case_when(age >= 18 & age <= 34 ~ "18-34",
                          age >= 35 & age <= 54 ~ "35-54",
                          age >= 55 ~ "55 plus",
                                TRUE ~ as.character(age)))
cjdt$Age <- factor(cjdt$age2)
mm_by <- cj(cjdt, fm, id = ~response_id, h0 = 0.5,
            estimate = "mm", by = ~Age)

# Plot
plot(mm_by, group = "Age", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8, begin = 0.25)
```
\normalsize

### Race

Below are our results when we disaggregate the data by race. We find that they are
almost identical is all dimensions except for offense. Asian respondents are
much less likely to select profiles that contain pickpocketing as a crime.

\footnotesize
```{r conjoint-race, warning=F, message=F, error=F, cache=T, fig.width=7, fig.height=7}
# Model
cjdt <- full_join(conjoint_data, df1, by = "response_id") %>%
  drop_na(race) %>%
  filter(race == c("Asian", "Black", "Mixed Race", "White"))
cjdt$Race <- factor(cjdt$race)
mm_by <- cj(cjdt, fm, id = ~response_id, estimate = "mm",
            h0 = 0.5, by = ~Race)

# Plot
plot(mm_by, group = "Race", vline = 0.5, header_fmt = "%s") +
  theme(legend.position = "bottom", axis.text.y = element_text(face = faces, size = 10)) +
  scale_colour_viridis_d(option = "inferno", end = 0.8)

# Tables
mm_asian <- mm_by %>% filter(BY == "Asian")
table_mm_by(mm_asian, capt = "Marginal Means -- Asian")
mm_black <- mm_by %>% filter(BY == "Black")
table_mm_by(mm_black, capt = "Marginal Means -- Black")
mm_mixed <- mm_by %>% filter(BY == "Mixed Race")
table_mm_by(mm_mixed, capt = "Marginal Means -- Mixed Race")
mm_white <- mm_by %>% filter(BY == "White")
table_mm_by(mm_white, capt = "Marginal Means -- White")
```
\normalsize
